The instability of variational quantum mechanics with Gaussian approximants is (not) entirely due to the unstable least squares problem

### 2013-06-13 paper.tex
stiffness of Schrodinger equation demonstrated

The first attempt at this will compute the dynamics of a quartic oscillator, with Hamiltonian 
$$H=\hbar a^{2\dagger}a².$$
It will do so by the midpoint method, discretising the differential equation
$$Du(t)=f(t)$$
to the difference equation
$$v^{n+1}=v^{n-1}+2τfⁿ,$$
where $tⁿ=nτ$, $vⁿ$ is meant to approximate $u(tⁿ)$, and $fⁿ=f(vⁿ)$.  The results will be compared for three difference choices of $v$ and $f$.

@@

>>>>

The first experiment computed the dynamics of a quartic oscillator, with Hamiltonian 
$$H=\hbar a^{2\dagger}a².$$
It used the explicit Euler formula, which discretises the differential equation
$$Du(t)=f(t)$$
to the difference equation
$$v^{n+1}=v^{n-1}+2τfⁿ,$$
where $tⁿ=nτ$, $vⁿ$ is meant to approximate $u(tⁿ)$, and $fⁿ=f(vⁿ)$.

@@

\centerline{\XeTeXpicfile dry.pdf width \hsize}
